\documentclass{article}
\usepackage{scimisc-cv}
\usepackage[hidelinks]{hyperref}

\title{Curriculum Vitae}
\author{Luis Fernando Nagua Cuenca}
\date{March 2025}

%% Custom CV Information
\cvname{Luis Fernando Nagua Cuenca, PhD}
\cvpersonalinfo{
Leganés 28912, Madrid, Spain \cvinfosep 
Mobile: +34 674859239 \cvinfosep 
mhlucho@gmail.com \cvinfosep   

\href{https://linktr.ee/mhlucho}{\textbf{Linktree}} \cvinfosep 
\href{https://linkedin.com/in/mhluchofer}{\textbf{LinkedIn}} \cvinfosep 
\href{https://scholar.google.com/citations?user=I6NYnWIAAAAJ&hl=es}{\textbf{Google Scholar}} \cvinfosep 
\href{https://orcid.org/0000-0002-1329-9780}{\textbf{ORCID}} \cvinfosep 

}

\begin{document}

\makecvtitle

\section{Summary}
\begin{itemize}
\item Researcher with experience in robotics, automation and mechatronics.
\item Expertise in soft robotics, machine learning and industrial automation.
\item Extensive knowledge of robotic system design, control and simulation.
\item Author of numerous peer-reviewed articles and conference papers.
\end{itemize}

\section{Technical Skills}
\begin{itemize}
    \item \textbf{Software:} SolidWorks, OpenCV, Matlab, ROS, RobotStudio.
    \item \textbf{Programming:} C++, Python, LaTeX.
    \item \textbf{Robotics:} Soft robotics, Industrial automation, Machine learning.
    \item \textbf{Control Systems:} CanOpen, Embedded Systems, Arduino.
\end{itemize}

\section{Education}
\begin{itemize}
    \item PhD in Robotics, University Carlos III of Madrid, 2018 – 2023.
    \item Master in Robotics and Automation, University Carlos III of Madrid, 2016 – 2018.
    \item Mechatronics Engineering, Universidad de las Fuerzas Armadas, 2007 – 2013.
\end{itemize}

\section{Professional Development}

\cvsubsection{Robotics Developer Masterclass}[The Construct Robotics Institute][sept 2025 -- Present]
\begin{itemize}
    \item Advanced practical training in ROS2, C++ applied to robotics, URDF modeling, TF2 transforms, launch files, multi-robot systems, and simulation.
    \item Hands-on projects integrating control, software development, and intelligent robotic systems.
    \item Projects and exercises available on GitHub. 
\end{itemize}

\section{Research Experience}

\cvsubsection{Postdoctoral Researcher}[Carlos III University of Madrid][Sep 2025 – present][Leganes, Spain]
\begin{itemize}
    \item Design and control of soft links for humanoid robots.
\end{itemize}

\cvsubsection{Postdoctoral Researcher}[ARQUIMEA Research Center][Oct 2023 – May 2025][Tenerife, Spain]
\begin{itemize}
            \item The development, simulation, and analysis of advanced robotic platforms for biomechanical and commercial applications, including wearable exoskeletons.
            
            \item The design and implementation of adaptive, gait-synchronized control algorithms for exoskeletons:
            \begin{itemize}
                \item Generation of sinusoidal torque profiles for actuators, initiated at heel strike.
                \item Real-time adaptation of torque profiles to human walking rhythm, using hip-based modeling and Fourier series analysis on the latest three cycles per 10-second window.
            \end{itemize}
            
            \item Integration of machine learning techniques to classify human movement patterns and phases, enhancing human-robot interaction and exoskeleton performance.
            
            \item Development of embedded systems using microcontrollers (I2C/SPI) and inertial sensors (IMU) for real-time motion tracking and control.
            
            \item Creation of interactive GUIs using Tkinter and ROS2 for monitoring and real-time visualization of robotic and exoskeleton platforms.
            
            \item Experimental validation of exoskeleton controllers to ensure safety, reliability, and biomechanical accuracy.
            
            \item Production of comprehensive technical documentation, including the architecture of the system, the algorithms, and the experimental results.
\end{itemize}

\cvsubsection{Predoctoral Researcher}[Carlos III University of Madrid][Sep 2018 – Aug 2023][Leganes, Spain]
\begin{itemize}
    \item Design and control of soft links for humanoid robots.
\end{itemize}

\cvsubsection{Scuola Superiore Sant’Anna}[Pontedera, Toscana, Italy]
[Visiting Pre-doctoral Student][Mar 2021 – Jun 2021]

\begin{itemize}
    \item Contributed to research in robotics and automation.
\end{itemize}

\cvsubsection{University Carlos III of Madrid}[Leganés, Spain]
[Intern Robotics Research Assistant][Jan 2017 – Aug 2018]

\begin{itemize}
    \item Humasoft Project: Designed and simulated a robotic neck prototype.
\end{itemize}


\section{Professional Experience}

\cvsubsection{Metas del Ecuador Cia. Ltda.}[Quito, Ecuador]
[Co-Founder \& Laboratory Technician][Oct 2015 – Feb 2018]

\begin{itemize}
    \item Developed procedures and technical studies in the Technical Area.
\end{itemize}

\cvsubsection{Vym S.A.}[Quito, Ecuador]
[Design Engineer][Feb 2016 – Jun 2016]

\begin{itemize}
    \item Designed and machined parts on CNC milling machines using code generated from SolidWorks and NX 8.0 Siemens.
\end{itemize}

\section{Teaching Experience}
\begin{itemize}
    \item Industrial Robotics Laboratory (110h), 2018 – 2023.
    \item Control Engineering – Exercises \\ \& Laboratory (104h), 2019 – 2023.
\end{itemize}

\section{Publications}

\subsection{Journal Articles}
\begin{itemize}
    \item L. Nagua, C. Relaño, C. A. Monje, and C. Balaguer, “A new approach of soft joint based on a cable-driven parallel mechanism for robotic applications,” \textit{Mathematics}, vol. 9, no. 13, p. 1468, 2021.
    \item L. Mena, C. A. Monje, L. Nagua, J. Muñoz, and C. Balaguer, “Test bench for evaluation of a soft robotic link,” \textit{Frontiers in Robotics and AI}, vol. 7, p. 27, 2020.
    \item J. Munoz, C. A. Monje, L. F. Nagua, and C. Balaguer, “A graphical tuning method for fractional order controllers based on isoslope phase curves,” \textit{ISA Transactions}, vol. 105, pp. 296–307, 2020.
    \item L. Mena, C. Monje, L. Nagua, J. Muñoz, and C. Balaguer, “Sensorización de un sistema de eslabón blando actuando como cuello robótico,” \textit{Actas de las Jornadas Nacionales de Robótica}, vol. 6, pp. 98–102, 2019.
    \item L. Nagua and P. Tupiza, “Diseño y construcción de un prototipo automático para rehabilitación pasiva de lesión por esguince de tobillo,” 2015.
\end{itemize}

\subsection{Conference Proceedings}
\begin{itemize}
    \item L. Nagua, N. Continelli, C. A. Monje, S. M. de la Casa, and C. Balaguer, “Machine learning techniques for the identification of a soft robotic neck,” in \textit{2022 IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS)}, (Poster), IEEE, 2022.
    \item L. Nagua, J. Muñoz, L. Mena, C. A. Monje, and C. Balaguer, “Robust control strategy for improving the performance of a soft robotic link,” in \textit{XLII Jornadas de Automática}, Universidade da Coruña, Servizo de Publicacións, 2021, pp. 499–506.
    \item L. Nagua, C. Monje, J. M. Yañez-Barnuevo, and C. Balaguer, “Design and performance validation of a cable-driven soft robotic neck,” in \textit{Proc. Actas de las Jornadas Nacionales de Robótica}, 2018, pp. 1–5.
    \item L. Nagua, J. Munoz, C. A. Monje, and C. Balaguer, “A first approach to a proposal of a soft robotic link acting as a neck,” in \textit{XXXIX Jornadas de Automática}, Área de Ingeniería de Sistemas y Automática, 2018.
\end{itemize}

\section{Patents}
\begin{itemize}
    \item \textbf{Eslabón para articulación blanda y articulación blanda que comprende dicho eslabón}  
    \textit{Expedida el 19 de junio de 2024, Ref. 2891180}
\end{itemize}

\section{Achievements}
\begin{itemize}
    \item \textbf{PhD: Classification of Excellent} \\  
          Cum laude mention - July 2023
    \item \textbf{Predoctoral Fellowship} \\  
          Ministry of Science and Innovation.  
          Predoctoral Fellowship (FPI).
\end{itemize}

\section{Languages}
\begin{itemize}
    \item Spanish: Native
    \item English: Professional
    \item German: Basic
\end{itemize}

\section{Referees}
\cvsubsection{Prof. Concepción A. Monje}
\textit{Universidad Carlos III de Madrid}  
Email: cmonje@ing.uc3m.es  
Address: Av. Universidad 30, 28911, Leganés - Madrid, Spain  
Phone: +34 916 246 013  


\end{document}

